---
output:
  html_document: default
  pdf_document: default
---
```{r}
# ---- Cleanup everything before start ----
options(warn=-1)
options(repos="https://cran.rstudio.com" )
rm(list = ls())
gc()
list.of.packages <- c("FSelector", "ggplot2")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos="http://cran.rstudio.com/")
library(FSelector)
library(ggplot2)
library(RWeka)
install.packages("repr")
library(repr)

#---- GBSERVER API ----
source("./Rscript/experimentAPI.R")
# ---- INPUT and CONFIGURATIONS ----

EDGE_TYPE_FILE = "./data/infobox.edgetypes" 
CLUSTER_SIZE = 2 # Number of workers in gbserver
FALSE_PER_TRUE = 5
DISCARD_REL = 191
ASSOCIATE_REL = c(404)
max_depth = 3

# ---- Load edge type file ----
mapfile <- read.csv(EDGE_TYPE_FILE, sep="\t", header=F)
mapfile$V1 <- as.numeric(mapfile$V1)
mapfile$V2 <- as.character(mapfile$V2)
```

### Find true capital-state pairs from:
(1) possible capital-state pairs
We have 50 true US capital-state. We then create 200 false pairs by random matching of capitals to states.
(2) possible capital-state and largestcity-state pairs
We have 50 true US capital-state. We then create 216 false pairs by matching each state to its largest city.
(3) possible capital-state and capital-country
We have 25 true US capital-state and 25 true capital country. We then create 200 false pairs by random matching of capitals to states or countries.


## Test case 1: 50 true US capital-state and 250 US false capital-state

```{r}
# ---- Load input data ----
INPUT_FILE = "./data_id/state_capital.csv"  
dat_state_capital.true <- read.csv(INPUT_FILE)
if (ncol(dat_state_capital.true) < 3)
  dat_state_capital.true$label <- T

# ---- Construct false labeled data -----
set.seed(233)
dat_state_capital.false <- rbind.fill(apply(dat_state_capital.true, 1, function(x){
  candidates <- unique(dat_state_capital.true[which(dat_state_capital.true[,1] != x[1]), 2])
  candidates <- unlist(lapply(candidates, function(y){
    if(length(which(dat_state_capital.true[,1] == x[1] & dat_state_capital.true[,2] == y) != 0)) {
      return(NULL)
    }
    return(y)
  }))
  return(data.frame(src=x[1], 
                    dst=sample(candidates, FALSE_PER_TRUE),
                    label=F))
}))
colnames(dat_state_capital.true) <- c("src","dst","label")
dat_state_capital <- rbind(dat_state_capital.true, dat_state_capital.false)
```

# Test 1: Discriminative predicate paths 
```{r}
tmp.paths <- read.csv("./Predicate_paths/capitals_1.csv", header = T)
tmp.paths$X <- NULL
dkm <- read.csv("./Predicate_paths/capitals_1.csv", header = F)
dkm$V1 <- NULL
colnames(tmp.paths) <- as.character(unlist(dkm[1,]))
```

# Test 1: 10 fold cross validation ( using all possible predicate paths) 
```{r}
res_capital_state<- list()
res_capital_state[["raw"]] <- tmp.paths
res_capital_state[["model"]] <- Logistic(label~.,res_capital_state[["raw"]])
res_capital_state[["eval"]] <- evaluate_Weka_classifier(res_capital_state[["model"]], numFolds = 10, complexity = T, class = T, seed = 233)
res_capital_state[["eval"]]
```

# Test 1: Feature selection validation (weighing predicate paths basing on their correlation with labels) 
```{r}
# ---- Feature selection validation ----
weights_capital_state <- information.gain(label~., res_capital_state[["raw"]])
weights_capital_state <- weights_capital_state[order(weights_capital_state[,1], decreasing = T),,drop=F]

# ---- Top related relations ----
features_captial_state <- data.frame(importance=weights_capital_state$attr_importance, path=row.names(weights_capital_state))

features_captial_state <- features_captial_state[order(-features_captial_state$importance),]

features_captial_state$path <- idpath2title(features_captial_state$path, mapfile)
weights_capital_state
head(weights_capital_state)
features_captial_state
head(features_captial_state)
```

# Test 1:Cross validation of impact of top discriminative path of classification performance
# Calculate ROC area in term of number of retained top paths
```{r}
# ---- AOROC of predicated sub paths ----
fm_val <- function(resdf) {
  return(as.numeric(str_split(str_split(resdf$eval$string,"\n")[[1]][24], " +")[[1]][9]))
}
full_predicated_path <- res_capital_state[["raw"]]
cl <- makeCluster(2) 
clusterExport(cl = cl, varlist=c("full_predicated_path", "weights_capital_state", "eval.df", "cutoff.k", "fm_val","str_split","as.numeric"), envir = environment())

res_AOROC <- rbind.fill(parLapply(cl, seq(1,ncol(full_predicated_path)-1,by = 5), function(x){
library(FSelector)
library(RWeka)
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state, x))])
return(data.frame(AOROC=fm_val(wekares),nfeature=x))
}))
stopCluster(cl)
```

```{r}
ggplot(data=res_AOROC, aes(x=nfeature, y=AOROC, group=1)) +
  geom_line(color="red")+
  geom_point()
```

# Test 1: 10 fold cross validation ( only use top 10 predicate paths) 
# Easily to classify False pair even using a few of discriminative paths, since in general, there is very few paths between 2 entities in false pairs.
# Misclassify some true pairs. Some of top 10 paths are trivial. May need another more efficient way to retrieve top paths
```{r}
full_predicated_path <- res_capital_state[["raw"]]
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state, 10))])
res_capital_state[["raw"]]
features_captial_state[c(1:10),]
wekares[["eval"]]
```



## Test case 2: 50 true US capital-state and 216 US largestcity-state pairs considered as false capital-state

```{r echo=FALSE, message=FALSE, warning=FALSE}
# ---- Load input data ----
INPUT_FILE = "./data_id/state_capital.csv" 
dat_state_capital.true <- read.csv(INPUT_FILE)
if (ncol(dat_state_capital.true) < 3)
  dat_state_capital.true$label <- T

# ---- Construct false labeled data -----
set.seed(233)
INPUT_FILE = "./data_id/state_largest_cities_id.csv" 
largest_cities <- read.csv(INPUT_FILE)

# TODO: reformat this so it is universal and file independent
dat_state_capital.false <- rbind.fill(apply(dat_state_capital.true, 1, function(x){
  candidates <- unique(largest_cities[which(largest_cities[,1] == x[1] & largest_cities[,2] != x[2]), 2])

  return(data.frame(src=x[1], 
                    dst=candidates,
                    label=F))
}))

colnames(dat_state_capital.true) <- c("src","dst","label")
dat_state_capital_largestcity <- rbind(dat_state_capital.true, dat_state_capital.false)
```

# Test 2: Discriminative predicate paths for test 2
```{r}
tmp.paths <- read.csv("./Predicate_paths/capitals_3.csv")
tmp.paths$X <- NULL
dkm <- read.csv("./Predicate_paths/capitals_3.csv", header = F)
dkm$V1 <- NULL
colnames(tmp.paths) <- as.character(unlist(dkm[1,]))
```

# Test 2: 10 fold cross validation ( using all possible predicate paths)
# Misclassify both some true & false pairs. Since capital-state and largest-city share many same paths (ex. location, birthplace..) -> take into account all possible paths may lead to misclassification. 
```{r}
res_capital_state_largestcity <- list()
res_capital_state_largestcity[["raw"]] <- tmp.paths
res_capital_state_largestcity[["model"]] <- Logistic(label~.,res_capital_state_largestcity[["raw"]])
res_capital_state_largestcity[["eval"]] <- evaluate_Weka_classifier(res_capital_state_largestcity[["model"]], numFolds = 10, complexity = T, class = T, seed = 233)
res_capital_state_largestcity[["eval"]]
```

# Test 2: Feature selection validation (weighing predicate paths basing on their correlation with labels)
```{r}
# ---- Feature selection validation ----
weights_capital_state_largestcity <- information.gain(label~., res_capital_state_largestcity[["raw"]])
weights_capital_state_largestcity <- weights_capital_state_largestcity[order(weights_capital_state_largestcity[,1], decreasing = T),,drop=F]

# ---- Top related relations ----
features_captial_state_largestcity <- data.frame(importance=weights_capital_state_largestcity$attr_importance, path=row.names(weights_capital_state_largestcity))

features_captial_state_largestcity <- features_captial_state_largestcity[order(-features_captial_state_largestcity$importance),]

features_captial_state_largestcity$path <- idpath2title(features_captial_state_largestcity$path, mapfile)
weights_capital_state_largestcity
head(weights_capital_state_largestcity)
features_captial_state_largestcity
head(features_captial_state_largestcity)
```

# Test 2: Cross validation of impact of top discriminative path of classification performance
# Calculate ROC area in term of number of retained top paths
```{r}
# ---- AOROC of predicated sub paths ----
fm_val <- function(resdf) {
  return(as.numeric(str_split(str_split(resdf$eval$string,"\n")[[1]][24], " +")[[1]][9]))
}
full_predicated_path <- res_capital_state_largestcity[["raw"]]
cl <- makeCluster(2) 
clusterExport(cl = cl, varlist=c("full_predicated_path", "weights_capital_state_largestcity", "eval.df", "cutoff.k", "fm_val","str_split","as.numeric"), envir = environment())

res_AOROC_largestcity <- rbind.fill(parLapply(cl, seq(1,ncol(full_predicated_path)-1,by = 5), function(x){
library(FSelector)
library(RWeka)
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state_largestcity, x))])
return(data.frame(AOROC=fm_val(wekares),nfeature=x))
}))
stopCluster(cl)
```

# Some first paths may have more useful information.
```{r}
ggplot(data=res_AOROC_largestcity, aes(x=nfeature, y=AOROC, group=1)) +
  geom_line(color="red")+
  geom_point()
```

# Test 2: 10 fold cross validation ( only use top 6 predicate paths) 
# Clear improvement in classification of false pairs -> show that these paths are really discriminative. 
# But using only these paths seems not enough for classification of true pairs. May need more paths.
```{r}
full_predicated_path <- res_capital_state_largestcity[["raw"]]
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state_largestcity, 6))])
features_captial_state_largestcity[c(1:6),]
wekares[["eval"]]
```

# Test 2: 10 fold cross validation ( only use top 21 predicate paths) 
# Good improvement in classification of true pairs without bad impact on false pairs when increasing number of paths
# -> show that we can find more discriminative paths
```{r}
full_predicated_path <- res_capital_state_largestcity[["raw"]]
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state_largestcity, 21))])
features_captial_state_largestcity[c(1:21),]
wekares[["eval"]]
```

# Test 2: 10 fold cross validation ( only use 11 selective predicate paths) 
# However, in first 20 paths (for ex.), there're still some trivial paths (ex. location, birthplace, deathplace..), we try to # remove them and add other non-trivial path (ex. assembly)
```{r}
full_predicated_path <- res_capital_state_largestcity[["raw"]]
wekares<-eval.df(full_predicated_path[,c("label", row.names(weights_capital_state_largestcity)[c(1,2,3,4,5,6,8,11,12,13,24)])])
features_captial_state_largestcity[c(1,2,3,4,5,6,8,11,12,13,24),]
wekares[["eval"]]
```


# Test 2: 10 fold cross validation ( only use top 11 predicate paths) 
# compare with above result in case of using 11 first paths.
```{r}
full_predicated_path <- res_capital_state_largestcity[["raw"]]
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state_largestcity, 11))])
features_captial_state_largestcity[c(1:11),]
wekares[["eval"]]
```


## Test case 3: 25 true US capital-state + 25 true capital-country and 250 US false capital-state + capital-country

```{r}
# ---- Load input data ----
INPUT_FILE = "./data_id/state_capital.csv"  
dat_state_capital.true <- read.csv(INPUT_FILE)
if (ncol(dat_state_capital.true) < 3)
  dat_state_capital.true$label <- T

INPUT_FILE = "./data_id/country_captial.csv"  
dat_country_capital.true <- read.csv(INPUT_FILE)
if (ncol(dat_country_capital.true) < 3)
  dat_country_capital.true$label <- T
dat_country_capital.true <- na.omit(dat_country_capital.true)

colnames(dat_state_capital.true) <- c("src","dst","label")
colnames(dat_country_capital.true) <- c("src","dst","label")
dat_state_capital_country.true <- rbind(dat_state_capital.true[c(26:50),], dat_country_capital.true[c(1:25),])

# ---- Construct false labeled data -----
set.seed(233)
dat_state_capital_country.false <- rbind.fill(apply(dat_state_capital_country.true, 1, function(x){
  candidates <- unique(dat_state_capital_country.true[which(dat_state_capital_country.true[,1] != x[1]), 2])
  candidates <- unlist(lapply(candidates, function(y){
    if(length(which(dat_state_capital_country.true[,1] == x[1] & dat_state_capital_country.true[,2] == y) != 0)){
      return(NULL)
    }
    return(y)
  }))
  return(data.frame(src=x[1], 
                    dst=sample(candidates, FALSE_PER_TRUE),
                    label=F))
}))
dat_state_capital_country <- rbind(dat_state_capital_country.true, dat_state_capital_country.false)
```

# Test 3: Discriminative predicate paths 
```{r}
tmp.paths <- read.csv("./Predicate_paths/capitals_4.csv", header = T)
tmp.paths$X <- NULL
dkm <- read.csv("./Predicate_paths/capitals_4.csv", header = F)
dkm$V1 <- NULL
colnames(tmp.paths) <- as.character(unlist(dkm[1,]))
```

# Test 3: 10 fold cross validation ( using all possible predicate paths) 
```{r}
res_capital_state_country<- list()
res_capital_state_country[["raw"]] <- tmp.paths
res_capital_state_country[["model"]] <- Logistic(label~.,res_capital_state_country[["raw"]])
res_capital_state_country[["eval"]] <- evaluate_Weka_classifier(res_capital_state_country[["model"]], numFolds = 10, complexity = T, class = T, seed = 233)
res_capital_state_country[["eval"]]
```

# Test 3: Feature selection validation (weighing predicate paths basing on their correlation with labels) 
```{r}
# ---- Feature selection validation ----
weights_capital_state_country <- information.gain(label~., res_capital_state_country[["raw"]])
weights_capital_state_country <- weights_capital_state_country[order(weights_capital_state_country[,1], decreasing = T),,drop=F]

# ---- Top related relations ----
features_captial_state_country <- data.frame(importance=weights_capital_state_country$attr_importance, path=row.names(weights_capital_state_country))

features_captial_state_country <- features_captial_state_country[order(-features_captial_state_country$importance),]

features_captial_state_country$path <- idpath2title(features_captial_state_country$path, mapfile)
weights_capital_state_country
head(weights_capital_state_country)
features_captial_state_country
head(features_captial_state_country)
```

# Test 1:Cross validation of impact of top discriminative path of classification performance
# Calculate ROC area in term of number of retained top paths
```{r}
# ---- AOROC of predicated sub paths ----
fm_val <- function(resdf) {
  return(as.numeric(str_split(str_split(resdf$eval$string,"\n")[[1]][24], " +")[[1]][9]))
}
full_predicated_path <- res_capital_state_country[["raw"]]
cl <- makeCluster(2) 
clusterExport(cl = cl, varlist=c("full_predicated_path", "weights_capital_state_country", "eval.df", "cutoff.k", "fm_val","str_split","as.numeric"), envir = environment())

res_AOROC_country <- rbind.fill(parLapply(cl, seq(1,ncol(full_predicated_path)-1,by = 5), function(x){
library(FSelector)
library(RWeka)
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state_country, x))])
return(data.frame(AOROC=fm_val(wekares),nfeature=x))
}))
stopCluster(cl)
```

```{r}
ggplot(data=res_AOROC_country, aes(x=nfeature, y=AOROC, group=1)) +
  geom_line(color="red")+
  geom_point()
```

```{r}
full_predicated_path <- res_capital_state_country[["raw"]]
wekares<-eval.df(full_predicated_path[,c("label", cutoff.k(weights_capital_state_country, 10))])
features_captial_state_country[c(1:10),]
wekares[["eval"]]
```